% frontmatter/abstract-en.tex — Abstract (English)
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\noindent\textbf{Title:} \thesistitleEN\\
\textbf{By:} \authornameEN\\
\textbf{Advisor:} \advisorEN, Ph.D.\\

At present, access to information through internet websites has become
increasingly popular and convenient due to advancements in modern technology,
particularly through web scraping techniques. Such data can be utilized to address
a wide range of practical problems. This project focuses on the development of an
automated system for extracting construction material price data from official
websites of the Ministry of Commerce, categorized by provinces where construction
projects are located, as well as from price announcements published by modern
trade retailers nationwide, such as HomePro, MegaHome, Boonthavorn, and Thai Watsadu.

The extracted data are subsequently used to calculate unit costs of construction
materials and to perform data analysis. Data management processes are also
implemented, including data cleaning, unit standardization, and matching
construction material items with similar characteristics across different
data sources. The data analysis emphasizes spatial and temporal comparisons of
unit costs of construction materials, as well as an assessment of the consistency
between government-announced prices and actual market unit costs obtained from
modern trade retailers.

The results of the study clearly illustrate trends and disparities in unit costs
of construction materials across different data sources. These findings can serve
as valuable supporting information for construction cost estimation, budget
planning, and decision-making processes for government agencies and relevant
stakeholders, thereby enhancing overall efficiency and effectiveness.

\noindent\textbf{Keywords:} Unit Cost, Construction Materials, Web Scraping, BOQ, Modern Trade, Ministry of Commerce
\newpage
